---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: "Christina Washington"
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
ggplot(covid_data_count, aes(x = date, y = Cases)) + geom_point()

ggplot(covid_data_long, aes(x = date, y = count)) + geom_point()
```


If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_count |> 
  filter(state == "MA") |> 
  ggplot(aes(x = date, y = Cases, color = race)) + geom_line()
```

1. Write code for a plot and describe what you observe?
```{r}
covid_data_count |> 
  filter(date == "2021-03-01" | date == "2021-03-07") |> 
  ggplot(aes(x = race, y = Cases, color = race)) + geom_line()
```
In this plot, I can observe the amount of cases that tested positive for COVID per race between the dates March 1st and March 7th. 

2. Are there any conclusions you can draw?

I can conclude that Lantins followed by Whites were most effected by Covid, and the other races were effected but not severely. 

3. What were you not able to do due to not having the R knowledge?
```{r}
covid_data_count |> 
  filter(date == "2021-03-07") |> 
  ggplot(aes(x = state, y = Cases, color = race)) + geom_line()
```

I did not know how to plot the data with an x-axis with states. Furthermore, it would be fun to know how to keep the x-axis as states but filter those as well. In other words, plot a graph that shows the Covid cases with the specific date of March 7th at the Massachusetts and New York states, colored by Race. 

4. What other data would be useful to better understand this data?

I think that population vs cases or deaths vs cases would also be useful to better understand this data by usingthe covid_data_orig. Graphs such as hosp vs deaths will also help us learn how many deaths there were relative to the amount of cases that needed hospitalization. 
